Sleep Quality Estimation using Accelerometer Data from Thigh-Mounted Devices During in Free Living Conditions

### 2023-03-16 presentation/index.qmd
roc curves are done. Next up is tables with all performance metrics.

<!-- ## ROC Curves {transition="convex"} -->
<!-- ### Two binary models (in-bed/asleep) -->

<!-- ```{r} -->
<!-- source(here::here("presentation/code/plot_roc_curves.R")) -->

<!-- roc_plots -->
<!-- ``` -->

<!-- ## ROC Curves {transition="convex"} -->
<!-- ### Binary relevance -->

<!-- ```{r} -->
<!-- source(here::here) -->
<!-- ``` -->

@@

<!-- ## References {transition="convex"} -->

>>>>

## ROC Curves {transition="convex"}

```{r}
source(here::here("presentation/code/plot_roc_curves.R"))

multi_roc_plot
```

## ROC Curves {transition="convex"}

```{r}
three_classifiers_roc_plot
```

## ROC Curves {transition="convex"}

```{r}
#| fig-width: 8
#| fig-align: center
two_classifiers_roc_plot
```

@@

## References {transition="convex"}
